COLLISION RATES OF PLANETESIMALS NEAR MEAN-MOTION RESONANCES

### 2019-08-06 main.tex
Add text to intro

\begin{abstract}
A perturbing planes can leave a lasting imprint a debris disk near the locations of mean motion resonances (MMRs). Unfortunately, the planetesimal-sized objects that make up the majority of these disks are extremely difficult to directly observe. Dust created from collisions between planetesimals may be a much better way to constrain the structure of these disks. We use a direct N-body model to measure planetesimal collision rates in a dynamically cold debris disk composed of 150 km bodies. Even though the eccentricities are pumped at the nominal resonance locations, conservation of the Jacobi energy pushes planetesimals inward and enhances the collision rate adjacent to the resonances. In addition, we find that the collision rate is severely throttled near the 3:1 MMR and that a tightly wound spiral wave is launched from this location.
\end{abstract}

@@

In some cases, these gap features are argued to be an indicator for the presence of a giant planet, either embedded in the disk \citep{2015MNRAS.453L..73D} or orbiting externally. An giant perturber can influence the structure of the dust emission in a number of ways. A misaligned giant planet can produce nonaxisymmetric features such as warps \citep{2001A&A...370..447A}. Highly eccentric perturbers can produce even more complicated structures through secular perturbations \citep{2014MNRAS.443.2541P, 2015MNRAS.448.3679P}. Mean motion resonances have been shown to open gaps as well \citep{2015ApJ...798...83N, 2016ApJ...818..159T, 2018ApJ...857....3T}.

The dynamics that give rise to second-generation dust in debris disks are not well understood. Add more text about this and some references. Should maybe discuss planet migration and resonant trapping here (and why we are ignoring it in our simulations)?

>>>>

\begin{abstract}
A perturbing planet can leave a lasting imprint a debris disk near the locations of mean motion resonances (MMRs). Unfortunately, the planetesimal-sized objects that make up the majority of these disks are extremely difficult to directly observe. Dust created from collisions between planetesimals may be a much better way to constrain the structure of these disks. We use a direct N-body model to measure planetesimal collision rates in a dynamically cold debris disk composed of 150 km bodies. Even though the eccentricities are pumped at the nominal resonance locations, conservation of the Jacobi energy pushes planetesimals inward and enhances the collision rate adjacent to the resonances. In addition, we find that the collision rate is severely throttled near the 3:1 MMR and that a tightly wound spiral wave is launched from this location.
\end{abstract}

@@

In some cases, these gap features are argued to be an indicator for the presence of a giant planet, either embedded in the disk \citep{2015MNRAS.453L..73D} or orbiting externally. An giant perturber can influence the structure of the dust emission in a number of ways. A misaligned giant planet can produce nonaxisymmetric features such as warps \citep{2001A&A...370..447A}. Highly eccentric perturbers can produce even more complicated structures through secular perturbations \citep{2014MNRAS.443.2541P, 2015MNRAS.448.3679P}. Mean motion resonances (MMRs) have been shown to open gaps as well \citep{2015ApJ...798...83N, 2016ApJ...818..159T, 2018ApJ...857....3T}.

The dynamics governing the motion of bodies near MMRs is extremely nonlinear, as is determining what the collision rates between planetesimals should look like in these regions. For a collection of bodies massive enough to experience the effects of gravitational focusing, a large eccentricity dispersion tends to reduce the probability of collision, while enhancements in surface density tends to increase it. Due to conservation of the Jacobi energy, MMRs simultaneously enhance the local eccentricity dispersion and also enhance the surface density adjacent to the resonance \citep{2000Icar..143...45R, 2017ApJ...850..103B}.

Because the second generation dust production is driven by the planetesimal collision rate, it is crucial to understand how the dynamics that drive collisions works. In particular, it is not obvious how to link the readily observable thermal emission from dust in protoplanetary disks to the presence of a perturbing giant planet. Due to its nonlinearity, this problem is best studied with N-body simulations. Unfortunately, collision detection in an N-body simulation is extremely computationally expensive. So far, studies of planetesimal dynamics near MMRs have involved either collisionless test particles \citep{2017ApJ...850..103B, 2016ApJ...818..159T, 2018ApJ...857....3T} or severely limited integration times \citep{2000Icar..143...45R}.

To further elucidate this subject, we use the tree based N-body code {\sc ChaNGa} \citep{2008IEEEpds...ChaNGa, 2015AphCom..2..1} to follow the collisional evolution of a planetesimal disk under the gravitational influence of a Jupiter sized body. Because particle positions are sorted into a tree structure, neighbor finding and collision detection can be done quickly and efficiently. This considerably relaxes the constraints on resolution and integration time. With this toolset, we explore the collision rate structure of the planetesimal disk in the vicinity of mean motion resonances.

This work is organized in the following way.
